Refinements for open automata

### 2022-04-15 2021-Refinement/paper/refinementarticle.tex
ajout figues
meeting notes

The next to theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation. This can be split into theorems that can be trivially composed by transitivity.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

@@

@@

@@

>>>>

The next two theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation. This can be split into theorems that can be trivially composed by transitivity.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

@@

\begin{center}
\includegraphics[scale=0.7]{Figures/Theorem2}
\end{center}

@@

\begin{center}
\includegraphics[scale=0.7]{Figures/Theorem1}
\end{center}

@@

TODO: FOCUS on the two following items (look at quentin's article):
